% Preamble
% ---
\documentclass[9pt,oneside]{memoir}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{scrextend}
\usepackage{calc}
\usepackage{tabularx}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.5in,bmargin=.5in,lmargin=.5in,rmargin=.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\newcommand{\name}{Clay McGinnis}
\newcommand{\email}{careers@clay.sh}
\newcommand{\github}{https://github.com/ClayMav}
\newcommand{\website}{https://clay.sh}

\newcommand{\cgpa}{3.5}


\begin{document}
\fontfamily{ppl} \selectfont

\begin{center}
      \textbf{\HUGE{\name}}\\
      \vspace{2px}
      \email\hspace*{10px}::\hspace*{10px}\url{\website}\hspace*{10px}::\hspace*{10px}\url{\github}\\
\end{center}

\vspace{3pt} \rule{\textwidth}{1pt}\vspace{6pt}

\vspace*{-14px}
\subsection*{Experience:}

\begin{itemize}
      \item[] \textbf{Amazon - Alexa Communications}
            \hfill Seattle, WA\\
            \textit{\textbf{Software Development Engineer I}}
            \hfill May. 2021 --- Nov. 2022
            \begin{itemize}
                  \item[\textbullet] Facilitated 300,000+ customer calls by building services to enable Roadside Assistance through Alexa in Java
                  \item[\textbullet] Reduced bi-weekly manual deployment time by 5 hours by converting 3 services to CI/CD involving the creation of integration tests, monitoring, and infrastructure built in AWS 
                  \item[\textbullet] Enabled 16,000+ new customer setups for Roadside Assistance and Emergency Calling with Alexa by building mobile app screens in the Alexa App using React Native with TypeScript
            \end{itemize}
      
      \item[] \textbf{Amazon - Alexa Communications}
            \hfill Seattle, WA\\
            \textit{\textbf{Software Development Engineer Intern}}
            \hfill May. 2020 --- Aug. 2020
            \begin{itemize}
                  \item[\textbullet] Enabled the resolution of 30+ customer tickets by modernizing our Java service metrics publishing library used for 600,000+ customer calls per month
                  \item[\textbullet] Identified 20+ previously undiscovered customer issues by creating dashboards and alarms
            \end{itemize}

      \item[] \textbf{CEADS-LIN:\@ Cybersecurity and Evolutionary Computing Research}
            \hfill Rolla, MO\\
            \textit{\textbf{Research Assistant} with Dr. Daniel Tauritz}
            \hfill Feb. 2018 --- Aug. 2019
            \begin{itemize}
                  \item[\textbullet] Created visualization tools in React.js to
                        monitor containerized network traffic and analyze evolutionary experiments
                        in real time
            \end{itemize}

      \item[] \textbf{Edward Jones Investments}
            \hfill St. Louis, MO\\
            \textit{\textbf{Software Engineering Intern}}
            \hfill May. 2019 --- Aug. 2019
            \begin{itemize}
                  \item[\textbullet] Fixed issues in 700,000+ customer calls per day by fixing MVC front-end bugs using JavaScript and Java
                  \item[\textbullet] Allowed for 3,000+ employees to move to a secure web browser by fixing website incompatibility problems for 4 core websites in JavaScript
            \end{itemize}

      \item[] \textbf{Stratos}
            \hfill Jan. 2021 - Present\\
            \textit{Personal Project - On-demand dedicated game servers as a service. No configuration required, controlled using a first party desktop app}
            \begin{itemize}
                  \item[\textbullet] Stratos was created to solve friction when gamers host dedicated servers. The Stratos desktop app and hosting service streamlines the experience in simplicity, pricing, and performance
                  \item[\textbullet] Designed the desktop app and website in Figma and built the website using Remix.js and React.js
                  \item[\textbullet] Designed and constructed the user facing API for payments, authentication, and managing servers and accounts using Golang, GraphQL (gqlgen), Auth0, and Stripe
                  \item[\textbullet] Designed back end infrastructure using Nomad, S3, and DigitalOcean Droplets to host internal services as well as customer game servers
                  \item[\textbullet] Built a service for automatic network population of DNS records in Cloudflare from Consul service entries with Golang
            \end{itemize}
\end{itemize}

\vspace*{-16px}
\subsection*{Education:}

\begin{itemize}
      \item[] Missouri University of Science and Technology (Missouri S\&T)
            \hfill \textbf{December 2020}\\
            \textbf{B.S. Computer Science}
            \hfill \cgpa{} Cumulative GPA

\vspace*{-10px}
\subsubsection*{Honors and Activities:}

\begin{itemize}
      \item[\textbullet] ACM Vice President Internal
            \hfill Apr. 2018 - Apr. 2019\\
            \textit{Managed 7 organizations in funding, time-lines, and planning for events hosting 120+ attendees}
      \item[\textbullet] Megaminer AI
            \hfill Dec. 2017\\
            \textit{2nd place among 30+ other teams --- Programmed an AI to play a game in Python}
\end{itemize}
   
     \vspace*{-1px}
      \item[] \textbf{Missouri S\&T --- Multirotor Robot Design Team}
            \hfill Rolla, MO\\
            \textit{\textbf{Chief Software Engineer}}
            \hfill Feb. 2019 --- May 2020
            \begin{itemize}
                  \item[\textbullet] Managed a team of 30+ software developers in
                        creating real-time autonomous software for an octo-copter in C++ and Python resulting in
                        acceptance to the International Aerial Robotics Competition
            \end{itemize}
            
      \item[] \textbf{Missouri S\&T --- ACM}
            \hfill Rolla, MO\\
            \textit{\textbf{ACM Web Chair}}
            \hfill Jan. 2020 --- Dec. 2020
            \begin{itemize}
                  \item[\textbullet] Managed and taught 14 students in building full-stack websites with React.js and mobile apps in React Native.
                  \item[\textbullet] Increased student event attendance up to 4x by building a full-stack website (link: \url{mstacm.org}) for ACM in TypeScript and React.js
            \end{itemize}

\end{itemize}

\vspace*{-11px}
\subsection*{Technical Skills:}

\begin{addmargin}[22pt]{0em}
      \begin{tabular*}{\textwidth - 22pt}{@{\extracolsep{\fill} } l l l l l l l l}
            \textbf{Languages:} & Golang & TypeScript & React.js & Python & C++ & Bash \\
            \textbf{Skills:} & Git & AWS & CI/CD & Unix & Unit/Integ Testing
      \end{tabular*}
\end{addmargin}

\end{document}
