% Preamble
% ---
\documentclass[10pt,oneside]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{scrextend}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.5in,bmargin=.5in,lmargin=.5in,rmargin=.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\newcommand{\name}{Clay McGinnis}
\newcommand{\phone}{(314) 587-6003}
\newcommand{\email}{mcginnis@claymav.com}
\newcommand{\github}{https://github.com/claymav}
\newcommand{\website}{https://claymav.com}

\newcommand{\cgpa}{3.34}
\newcommand{\mgpa}{4.00}

% Packages
% ---

\begin{document}
\fontfamily{ppl} \selectfont

\begin{center}
\textbf{\Huge{\name}}

\Large{\url{\github}}\\
\Large{\url{\website}}
\end{center}

\underline{\textbf{School Address}}
\hfill
\underline{\textbf{Home Address}}

900 Collegiate Blvd 2301
\hfill
239 Palisades Ridge Court

Rolla, MO 65401
\hfill
Eureka, MO 63025

\email
\hfill
\phone

\vspace{0pt} \rule{\textwidth}{1pt}

\vspace*{-16pt}
\section*{Education}
\vspace*{-4pt}

\begin{itemize}
	\item[] Missouri University of Science and Technology
			\hfill
			May 2020
			
    		\textbf{B.S. Computer Science}
			\hfill
			\textbf{GPA: \cgpa{} Overall, \mgpa{} Major}
    		\end{itemize}

\vspace*{-16pt}
\section*{Projects}
\vspace*{-4pt}
\begin{itemize}
	\item[] \textbf{Swoly:}
		\hfill
		Jan 2018
			\begin{itemize}
				\item[\textbullet] Fitness app that logs and computes weights to lift based on your personal bests.
				\item[\textbullet] Cooperated with another developer for the extent of the project.
				\item[\textbullet] Developed for Android in Java and SQLite
			\end{itemize}
	\item[] \textbf{ACM Website:} (\url{https://acm.mst.edu})
		\hfill
		Jan 2018
			\begin{itemize}
				\item[\textbullet] Designed the interface for the website.
				\item[\textbullet] Programmed the user-facing functionality of the site.
				\item[\textbullet] Developed for the web using Django, a Python framework, and HTML/CSS/JS in a small group.
			\end{itemize}
	\item[] \textbf{ShamHacks 2018:} Developed a business focused network for Military Veterans using Flask and SQLite (\textbf{2nd Place}, Team Project)
\end{itemize}

\vspace*{-16pt}
\section*{Experience}
\vspace*{-4pt}
\begin{itemize}
	\item[] \textbf{Missouri S\&T - ACM SIG.com}
			\hfill
			Rolla, MO
			
			\textit{\textbf{Vice Chair}}
			\hfill
			Aug 2016 - Present
			\begin{itemize}
				\item[\textbullet] Developed the front and back end of the Missouri S\&T ACM website.
				\item[\textbullet] Trained other members of the team in Python and web development skills.
				\item[\textbullet] Organized and led organization meetings and workshops.
				\item[\textbullet] Promoted events and activities through email, fliers, and the website.
			\end{itemize}
	\item[] \textbf{Target}
			\hfill
			Fenton, MO
			
			\textit{\textbf{Team Member}}
			\hfill
			Nov 2015 - Jan 2016
			\begin{itemize}
				\item[\textbullet] Supported customers with questions and requests.
				\item[\textbullet] Organized the sales floor.
				\item[\textbullet] Conducted a team for cleaning and organizing inventory on sales floor.
			\end{itemize}
	\end{itemize}

\vspace*{-16pt}
\subsection*{Technical Skills}
\begin{addmargin}[22pt]{0em}
	\begin{tabular*}{0.75\textwidth}{@{\extracolsep{\fill} } l l l l}
    		C++ & Git & Unix & Python \\ HTML/CSS & Javascript & Golang & R\\
	\end{tabular*}
\end{addmargin}

\subsection*{Honors and Activities}
\begin{itemize}
	\item[] Dean's List
		\hfill Fall 2017
		\vspace*{-7pt}
	\item[] ShamHacks Hackathon \textemdash{} \textbf{2nd Place}
		\hfill Feb 2018
		\vspace*{-7pt}
	\item[] MLH Local Hack Day Hackathon \textemdash{} 2nd Place
		\hfill Dec 2017
		\vspace*{-7pt}
	\item[] Megaminer AI
		\hfill Dec 2017
		\vspace*{-7pt}
	\item[] Association for Computing Machinery
		\hfill Aug 2016 - Present
		\vspace*{-7pt}
	\item[] Augmented Reality Research Group
		\hfill Sept 2017 - Present
		\vspace*{-7pt}
	\item[] Miner Village Hall Association
		\hfill Aug 2017 - Present
		\vspace*{-7pt}
	\item[] Miner Movies
		\hfill Dec 2017 - Present \hspace{1cm}
\end{itemize}

\end{document}