% Preamble
% ---
\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.5in,bmargin=.5in,lmargin=.5in,rmargin=.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\newcommand{\name}{Clay McGinnis}
\newcommand{\phone}{(314) 587-6003}
\newcommand{\email}{mcginnis@claymav.com}
\newcommand{\github}{https://github.com/claymav}
\newcommand{\website}{https://claymav.com}

% Packages
% ---

\begin{document}
\fontfamily{ppl} \selectfont

\begin{center}
\textbf{\Huge{\name}}

\Large{\url{\github}}\\
\Large{\url{\website}}
\end{center}

\underline{\textbf{School Address}}
\hfill
\underline{\textbf{Home Address}}

900 Collegiate Blvd 2301
\hfill
239 Palisades Ridge Court

Rolla, MO 65401
\hfill
Eureka, MO 63025

\email
\hfill
\phone

\vspace{0pt} \rule{\textwidth}{1pt}

\section*{Education}
\begin{itemize}
	\item[] Missouri University of Science and Technology
			\hfill
			Aug 2016 - Present
			
    		\textbf{In-progress B.S. Computer Science GPA: 3.34 (Overall), 4.00 (Major)}
    \item[] \textbf{Courses:}
    
    		\begin{tabular*}{0.75\textwidth}{@{\extracolsep{\fill} } l l l}
    			Introduction to C++ & Data Structures & Algorithms \\
				Discrete Mathematics & Contemporary Programming Languages & Databases \\
    		\end{tabular*}
\end{itemize}
\section*{Experience}
\begin{itemize}
	\item[] \textbf{Swoly:} Fitness app that logs and computes weights to lift based on your personal bests.
			\begin{itemize}
				\item[\textbullet] Developed for Android in Java and SQLite
			\end{itemize}
\end{itemize}
\begin{itemize}
	\item[] Missouri S\&T - ACM SIG.com
			\hfill
			Rolla, MO
			
			\textbf{Vice Chair}
			\hfill
			Aug 2016 - Present
			\begin{itemize}
				\item[\textbullet] Developed the front and back end of the Missouri S\&T ACM website.
				\item[\textbullet] Trained other members of the team in Python and web development skills.
				\item[\textbullet] Organized and led organization meetings and workshops.
				\item[\textbullet] Promoted events and activities through email, fliers, and the website.
			\end{itemize}
	\item[] Target
			\hfill
			Fenton, MO
			
			\textbf{Team Member}
			\hfill
			Nov 2015 - Jan 2016
			\begin{itemize}
				\item[\textbullet] Supported customers with questions and requests.
				\item[\textbullet] Organized the sales floor.
				\item[\textbullet] Conducted a team for cleaning and organizing inventory on sales floor.
			\end{itemize}
	\item[] Lakeview Park Independent Living
			\hfill
			Fenton, MO
			
			\textbf{Server}
			\hfill
			Aug 2015 - Dec 2015
			\begin{itemize}
				\item[\textbullet] Memorized details in bulk when serving.
			\end{itemize}
\end{itemize}
\section*{Technical Skills}
\begin{itemize}
	\item[] {\bfseries \itshape Strong:} Git, Unix, C++, Python, HTML/CSS
	\item[] {\bfseries \itshape Knowledgable:} Go, Javascript
\end{itemize}


\end{document}